Validation of Visual Statistical Inference, Applied to Linear Models

### 2012-06-08 paper_jasa.tex
added criteria 6 for screening data

% In this process of collecting data some participants did not provide demographic information as we see in Table \ref{tbl:summary} that male and female participants do not add up to total participants. It is not clear why they did not provide the information. Now the concern arises whether we should keep their responses in the study. It is also possible that participants were not serious enough to provide feedback. 
For each of the experiments we had a test plot (easy plot) for which they should have a correct evaluation without much effort.  This could be a criteria to determine their attentiveness in the study. For this we consider five different data cleaning criteria as shown below;

{\bf Cleaning data:} There are five suggested approach to clean the data. They are 
\begin{enumerate}
\item not throw out anything
\item throw out people where we don't have demographic information
\item throw out all people with 0 percent correct
\item only include people with at least 20 percent correct (current suggestion)
\item include people with 50\% correct on all very easy (could be evaluated correctly if the participant is not ignorant) lineups (as suggested before)
\end{enumerate}

\begin{table}[hbtp]
\caption{Number of unique subjects and their total feedbacks after applying five screening process on all three experimental data sets.}
\begin{center}
\begin{tabular}{rrrrr|rrrr|rrrr}
  \hline
Screening &  \multicolumn{4}{c} {Experiment 1}  & \multicolumn{4}{c} {Experiment 2}  & \multicolumn{4}{c} {Experiment 3} \\
 \cline{2-5}  \cline{6-9}   \cline{10-13}
criteria & Subj & Male & Fem & Total & Subj & Male & Fem & Total & Subj & Male & Fem & Total \\ 
  \hline
1 & 520 & 264 & 201 & 4914 & 390 & 203 & 182 & 4603 & 257 & 166 &  84 & 2830 \\ 
  2 & 465 & 264 & 201 & 4624 & 385 & 203 & 182 & 4558 & 250 & 166 &  84 & 2782 \\ 
  3 & 384 & 200 & 165 & 4187 & 384 & 199 & 181 & 4573 & 227 & 147 &  78 & 2648 \\ 
  4 & 318 & 168 & 135 & 3395 & 378 & 195 & 179 & 4492 & 205 & 133 &  72 & 2393 \\ 
  5 & 277 & 139 & 124 & 3008 & 374 & 193 & 177 & 4451 & 112 &  73 &  39 & 1410 \\ 
   \hline
\end{tabular}
\end{center}
\label{tbl:summary}
\end{table}

@@

\begin{figure}[hbtp]
   \centering
       \scalebox{0.70}{\includegraphics{power_screening.pdf}}
       \caption{The overall power estimated from model \ref{mixed} are shown for various data sets obtained by applying 5 screening criteria.  The corresponding power curve for Uniformly Most powerful (UMP) test is shown in black solid lines for comparison.}
       \label{fig:power_screening}
\end{figure}

@@

\begin{figure}[hbtp]
   \centering
       \scalebox{0.60}{\includegraphics{power_screening_subject.pdf}}
      \caption{The subject specific power estimated from model \ref{mixed} are shown for various data sets obtained by applying 5 screening criteria.  The corresponding power curve for Uniformly Most powerful (UMP) test is shown in pink lines for comparison.}
       \label{fig:power_screening_subject}	
\end{figure}

>>>>

% In this process of collecting data some participants did not provide demographic information as we see in Table \ref{tbl:summary} that male and female participants do not add up to total participants. It is not clear why they did not provide the information. Now the concern arises whether we should keep their responses in the study. It is also possible that participants were not serious enough to provide feedback. 
For each of the experiments we had a test plot (easy plot) for which they should have a correct evaluation without much effort.  This could be a criteria to determine their attentiveness in the study. For this we consider six different data cleaning criteria as shown below;

{\bf Cleaning data:} There are six suggested approach to clean the data. They are 
\begin{enumerate}
\item not throw out anything
\item throw out people where we don't have demographic information
\item throw out all people with 0 percent correct
\item only include people with at least 20 percent correct (current suggestion)
\item include people with 50\% correct on all very easy (could be evaluated correctly if the participant is not ignorant) lineups (as suggested before)
\item each person saw at least one easy lineup. we select one of those easy lineups as the inclusion criteria. If that lineup is evaluated correctly we include only the rest of the evaluations of that subject. Otherwise, we exclude all the feedbacks of that subject.
\end{enumerate}

\begin{table}[hbtp]
\caption{Number of unique subjects and their total feedbacks after applying six screening process on all three experimental data sets.}
\begin{center}
\begin{tabular}{rrrrr|rrrr|rrrr}
  \hline
Screening &  \multicolumn{4}{c} {Experiment 1}  & \multicolumn{4}{c} {Experiment 2}  & \multicolumn{4}{c} {Experiment 3} \\
 \cline{2-5}  \cline{6-9}   \cline{10-13}
criteria & Subj & Male & Fem & Total & Subj & Male & Fem & Total & Subj & Male & Fem & Total \\ 
  \hline
1 & 520 & 264 & 201 & 4914 & 390 & 203 & 182 & 4603 & 257 & 166 &  84 & 2830 \\ 
  2 & 465 & 264 & 201 & 4624 & 385 & 203 & 182 & 4558 & 250 & 166 &  84 & 2782 \\ 
  3 & 384 & 200 & 165 & 4187 & 384 & 199 & 181 & 4573 & 227 & 147 &  78 & 2648 \\ 
  4 & 318 & 168 & 135 & 3395 & 378 & 195 & 179 & 4492 & 205 & 133 &  72 & 2393 \\ 
  5 & 277 & 139 & 124 & 3008 & 374 & 193 & 177 & 4451 & 112 &  73 &  39 & 1410 \\ 
  6 & 239 & 121 & 107 & 2317 & 351 & 185 & 164 & 3858 &  98 &  64 &  34 & 1095 \\ 
   \hline
\end{tabular}
\end{center}
\label{tbl:summary}
\end{table}

@@

\begin{figure}[hbtp]
   \centering
       \scalebox{0.70}{\includegraphics{power_screening.pdf}}
       \caption{The overall power estimated from model \ref{mixed} are shown for various data sets obtained by applying 6 screening criteria.  The corresponding power curve for Uniformly Most powerful (UMP) test is shown in black solid lines for comparison.}
       \label{fig:power_screening}
\end{figure}

@@

\begin{figure}[hbtp]
   \centering
       \scalebox{0.60}{\includegraphics{power_screening_subject.pdf}}
      \caption{The subject specific power estimated from model \ref{mixed} are shown for various data sets obtained by applying 6 screening criteria.  The corresponding power curve for Uniformly Most powerful (UMP) test is shown in pink lines for comparison.}
       \label{fig:power_screening_subject}	
\end{figure}
